% =============================================================================
% Aaron Barlow - Professional Resume
% LaTeX Document Configuration and Custom Commands
% =============================================================================

% Document class and basic settings
% Using article class with 11pt font and A4 paper size for professional appearance
\documentclass[11pt,a4paper]{article}

% =============================================================================
% PACKAGE IMPORTS AND CONFIGURATION
% =============================================================================

% Font configuration - Using Georgia for a professional, readable appearance (similar to Cambria)
\usepackage{fontspec}
\setmainfont{Georgia}

% Page layout and spacing packages
\usepackage[margin=0.6in]{geometry}  % Set page margins to 0.6 inches for compact layout
\usepackage{enumitem}                % Enhanced list formatting
\usepackage{setspace}                % Line spacing control
\usepackage{xcolor}                  % Color support for custom styling

% =============================================================================
% DOCUMENT STYLING AND FORMATTING
% =============================================================================

% Remove paragraph indentation and set paragraph spacing for clean layout
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

% =============================================================================
% CUSTOM COMMAND DEFINITIONS
% =============================================================================

% Custom section command that creates a thick gray underline
% Usage: \resumesection{Section Name}
% Creates a bold section title with a 2pt gray rule underneath
\newcommand{\resumesection}[1]{
    \vspace{3pt}                                    % Add space before section
    \noindent{\fontsize{13}{15}\selectfont\textbf{#1}}\\[-8pt]                    % Bold section title with 2pt+ increase
    \noindent\textcolor{gray}{\rule{\textwidth}{2pt}}\\[-10pt]  % Gray underline
}

% Custom experience entry command for consistent formatting
% Parameters: #1 = Company/Institution, #2 = Date Range, #3 = Job Title, #4 = Location
% Usage: \experienceentry{Company}{Date Range}{Job Title}{Location}
\newcommand{\experienceentry}[4]{
    \vspace{2pt}                                    % Add space before entry
    \noindent\textbf{#1} \hfill #2\\               % Company name (left) and dates (right)
    \noindent{\fontsize{10}{12}\selectfont\textit{#3}} \hfill {\fontsize{10}{12}\selectfont\textit{#4}}\\               % Job title (italic, left) and location (right) with -1pt
    \vspace{1pt}                                    % Add space after entry
}

% Custom command for smaller font bullet points to save space
% Usage: \smallbullet{Bullet point text}
% Reduces font size to 9pt for more compact bullet points (additional -1pt)
\newcommand{\smallbullet}[1]{
    \item {\fontsize{9}{11}\selectfont #1}
}

% Custom command for regular bullet points with -1pt font size
% Usage: \regbullet{Bullet point text}
% Reduces font size to 10pt for regular bullet points
\newcommand{\regbullet}[1]{
    \item {\fontsize{10}{12}\selectfont #1}
}

% =============================================================================
% DOCUMENT CONTENT BEGINS
% =============================================================================

\begin{document}

% =============================================================================
% HEADER SECTION - Personal Information
% =============================================================================

% Centered header with name and contact information
\begin{center}
    {\fontsize{19}{23}\selectfont\textbf{AARON BARLOW}}\\[4pt]           % Large, bold name with 1pt increase
    865.804.6746  |  abarlow505@gmail.com  |  github.com/aroswift  |  aaronbarlow.dev\\[4pt]
\end{center}

% =============================================================================
% EXPERIENCE SECTION - Professional Work History
% =============================================================================

\resumesection{EXPERIENCE}

% Current position at Oak Ridge National Laboratory
\noindent\textbf{Oak Ridge National Laboratory — National Center for Computational Sciences (NCCS)}\\
\noindent{\fontsize{10}{12}\selectfont\textit{HPC Software Engineer}}  |  {\fontsize{10}{12}\selectfont\textit{Jun 2020--Present}}\\
\noindent{\fontsize{9}{11}\selectfont\textit{Scope:} Build researcher self-service and fleet operations software across \textbf{27 HPC clusters} (incl. Frontier), enforcing \textbf{policy-as-code} and secure access for a \textbf{\$700M+} compute footprint.}
\begin{itemize}[leftmargin=18pt,itemsep=1pt,topsep=0pt]
% Federated Learning project - Key technical achievement
\regbullet{Enabled \textbf{privacy-preserving federated learning at exascale} on \textbf{Frontier (first U.S. exascale system; TOP500 \#2)}, unlocking cross-institution healthcare data training on AMD GPUs. Brought NVFLARE to ROCm/MI250X with PyTorch (ROCm), produced HIP-compatible builds, packaged deterministic ROCm containers, and integrated with Slurm with mTLS inside secure enclaves. Validated multi-node training rounds previously not possible on Frontier. Now used to build \textbf{privacy-preserving medical foundation models} on Frontier.}

% Portal ownership and reliability achievements
\regbullet{Owned and scaled \textbf{myOLCF} (researcher self-service \& monitoring) used by \textbf{thousands (\~4k)} across \textbf{1,000+ projects} with \textbf{99.9\%+} availability. Shipped \textbf{12} FY2025 releases. Governs access, allocation, and policy across open, moderate, and secure enclaves.}

% Performance improvements with specific metrics
\regbullet{Replaced Jbuilder with a JSON\:API serializer and explicit Redis caching for hot read paths, taking the 100k-row directories endpoint from \~272s to \textbf{178--206 ms} on cached hits (0.206s avg) (≈\textbf{1320×}; −\textbf{99.92\%}) and improving first-hit from \textbf{298.5s} to \textbf{246.8s} (−\textbf{17\%}). Eliminated view-rendering cost (\~252s $\rightarrow$ \~0ms) and cut ActiveRecord time (\~19.2s $\rightarrow$ \textbf{8.8ms}). Stabilized fleet-wide polling and removed timeouts during cluster syncs.}

% Backend system development
\regbullet{Extended the Netflix-originated \textbf{fast\_jsonapi} fork (\textbf{jsonapi-serializer}) via `lib/library\_extensions/jsonapi\_serializer.rb` to support legacy root envelopes for V3/V4, runtime cache flags/TTLs, and per-record invalidation; enabling progressive rollout across endpoints.}

% Build and CI improvements
\regbullet{Accelerated build, startup, and test cycles by migrating to Vite and optimizing CI. Builds \textbf{2 min $\rightarrow$ 9 s (-92\%)}, startup \textbf{30 s $\rightarrow$ <200 ms (-99\%)}, tests \textbf{90 s $\rightarrow$ 6 s (-93\%)}. Cut developer idle time and sped up review cycles.}

% Smart Facility metrics platform
\regbullet{Built the \textbf{Smart Facility metrics platform} (backend in Crystal/Amber) ingesting compute/data/I/O/efficiency metrics; pre-aggregated dashboards deliver \textbf{100k-record} views with low latency and serve \textbf{\~50k time-series points in \~87 ms}. Benchmarked \~\textbf{10.4k req/sec per CPU core (\~96 µs/req)} for simple JSON. Shifted heavy computation to background jobs and index tables. Used by lab leadership to guide next-gen procurements (RAM/IO/GPU/storage priorities) and to benchmark domains, flagging inefficient Slurm jobs.}

% GitOps and Kubernetes
\regbullet{Standardized \textbf{GitOps delivery} with Kustomize + Argo CD on Kubernetes (GitLab runners), enabling declarative configs, drift correction, and one-click rollbacks across environments.}

% Policy-as-code service
\regbullet{Unified day-to-day operations across \textbf{27 HPC clusters} (incl. \textbf{Frontier}) via a central \textbf{policy-as-code} service. Automated project provisioning, access control, and scheduler policy across SLURM/LSF enclaves. Backbone software for a \textbf{\$700M+} compute fleet and mixed open $\rightarrow$ secure environments.}

% Automation and data integrity
\regbullet{Automated project lifecycle and data-integrity workflows, eliminating manual back-office corrections for project/application records.}

% Quality assurance and testing
\regbullet{Zero post-deploy incidents over the past 3 years by expanding Cypress/feature coverage and tightening parameter validation.}

% Leadership and mentoring
\regbullet{Mentored \textbf{3} interns/junior engineers; coached \textbf{100+} students through PEARC/SC workshops. Authored runbooks, SLOs, and incident playbooks.}
\end{itemize}

% Internship at Bank of America
\vspace{8pt}
\noindent\textbf{Bank of America — Consumer, Small Business \& Wealth Tech}\\
\noindent{\fontsize{10}{12}\selectfont\textit{ML Engineer Intern}}  |  {\fontsize{10}{12}\selectfont\textit{Jun--Aug 2019}}
\begin{itemize}[leftmargin=18pt,itemsep=1pt,topsep=0pt]
% NLP project with quantifiable results
\regbullet{Built an \textbf{NLP entity extraction service} (names/phones/addresses/accounts/amounts) at \textbf{96\% F1}, supporting \textbf{\$20M+/yr} in savings through automation}
\end{itemize}

% Previous internship at ORNL
\vspace{8pt}
\noindent\textbf{Oak Ridge National Laboratory — National Center for Computational Sciences (NCCS)}\\
\noindent{\fontsize{10}{12}\selectfont\textit{Software Developer Intern}}  |  {\fontsize{10}{12}\selectfont\textit{May 2015--May 2019}}
\begin{itemize}[leftmargin=18pt,itemsep=1pt,topsep=0pt]
% General development work
\regbullet{Year-round development of HPC-centric services, applications, and BI tools. Shipped production features across internal portals.}

% Automation project
\regbullet{Automated supercomputer access communications via a policy-aware email system. Standardized messaging and reduced manual steps.}

% WordPress plugin development
\regbullet{Built a WordPress/REST plugin to sync \& display HPC metrics on olcf.ornl.gov. Improved data freshness and reduced update toil.}
\end{itemize}

% =============================================================================
% SKILLS SECTION - Technical Competencies
% =============================================================================

\resumesection{SKILLS}

\begin{itemize}[leftmargin=18pt,itemsep=1pt,topsep=0pt]
% Programming languages
\regbullet{\textbf{Languages:} Ruby, Python, Go, TypeScript (Node), SQL, Bash}

% Backend technologies
\regbullet{\textbf{Back-end:} Rails, FastAPI/Flask, gRPC, REST, Redis, Postgres}

% Infrastructure and observability tools
\regbullet{\textbf{Infra/Obs:} Docker, Kubernetes, Kustomize, \textbf{Argo CD}, \textbf{Slurm}, CI/CD, Prometheus/Grafana, OpenTelemetry, \textbf{ROCm}, HashiCorp Vault, MinIO, KubeDB, Stash, SonarQube}

% Machine learning and federated learning infrastructure
\regbullet{\textbf{ML/FL Infra:} NVFLARE, PyTorch (ROCm), HIP}

% Agentic systems
\regbullet{\textbf{Agentic Systems:} multi-agent orchestration (\textbf{CrewAI} for Anthologia \& prediction-market system), autonomous pipelines, headless uploaders, queueing/retries}
\end{itemize}

% =============================================================================
% EDUCATION SECTION - Academic Background
% =============================================================================

\resumesection{EDUCATION}

% Educational background with GPA and honors
\noindent\textbf{East Tennessee State University} — Bachelor of Science, Computer Science | Dean's List | GPA \textbf{3.94/4.00} • May 2020\\
\noindent{\fontsize{9}{11}\selectfont Activities: \textbf{ACM (President, 2019--2020)}; \textbf{Ethical Hacking (Vice President, 2018--2019)}}

% =============================================================================
% SELECTED PROJECTS SECTION - Personal and Professional Projects
% =============================================================================

\resumesection{SELECTED PROJECTS}

\begin{itemize}[leftmargin=18pt,itemsep=1pt,topsep=0pt]
% AI-powered content creation projects
\regbullet{\textbf{Automatic movie creation (agentic pipeline)} — multi-agent workflow generates script $\rightarrow$ storyboard images $\rightarrow$ 10-sec clips (Runway/Cling) $\rightarrow$ stitches, QC, and \textbf{auto-publishes}.}

% Music and video automation
\regbullet{\textbf{Anthologia (AI video storytelling)} — multi-agent pipeline (\textbf{CrewAI}) turns concepts into \textbf{20-second} videos with \textbf{4 scenes}, using DALL·E 3 + Veo 3.0 (fallback Kling), ElevenLabs narration/SFX, and LatentSync lip sync; typical \textbf{4--12 min} per production with automated QC/fallbacks.}

% Music and video automation
\regbullet{\textbf{Project Cadenza (agentic music + video)} — agentic pipeline creates artists/albums, writes lyrics (GPT), generates songs (Suno/Udio), masters audio, produces thumbnails/art, and \textbf{auto-uploads to YouTube} with metadata/scheduling; \textbf{published 150 videos}; prepares ISRC/metadata for distributor workflows.}

% AI training automation
\regbullet{\textbf{Policy-driven data synthesizer (training automation)} — takes a policy/goal and \textbf{auto-creates synthetic training data} $\rightarrow$ trains/refits a model with quality guardrails.}

% E-commerce automation
\regbullet{\textbf{Automatic product creation (e-commerce)} — AI agents (GPT) and custom orchestration + Flux Pro image gen $\rightarrow$ vectorize/upscale $\rightarrow$ SEO titles/tags $\rightarrow$ \textbf{auto-publish} via Printful/Etsy and Redbubble; \textbf{152 products created} with \textbf{57k+ product views} to date; \textbf{cost ≈ \$0.31 per product}; database-driven workflow with retries and headless uploaders.}

% Music creation and distribution
\regbullet{\textbf{Automatic music video creation} — audio beat-map $\rightarrow$ storyboard $\rightarrow$ video assembly $\rightarrow$ captioning $\rightarrow$ render; \textbf{478 views} with \textbf{10.8 hours watched} on recent releases.}

% Podcast automation
\regbullet{\textbf{Automatic podcast creation} — multi-channel system (12+) with \textbf{Claude 3.5 Sonnet} scripts (7k+ words) $\rightarrow$ ElevenLabs TTS $\rightarrow$ audio assembly $\rightarrow$ \textbf{auto-publish} to Spreaker with metadata/scheduling; produces \textbf{6+ episodes per run} and has shipped \textbf{192 episodes}, totaling \textbf{\~1.8k downloads} and \textbf{50+ hours listened}.}

% Book creation automation
\regbullet{\textbf{Automatic book creation} — multi-agent pipeline (CrewAI) orchestrates GPT-4o-mini writing, Flux Pro/Replicate illustrations with vision-based QC, then compiles \textbf{print-ready PDF/EPUB} via ReportLab/LaTeX; metadata persisted in Firebase; typical cost \textbf{<\$5--10/book}.}

% AI prediction market trading system
\regbullet{\textbf{AI prediction-market trading system (Kalshi)} — multi-agent analysis (\textbf{CrewAI}) + real-time WebSocket feeds, vector DB, and Kelly sizing; selects market and executes end-to-end in \textbf{<6 minutes} (dev stage), with Dockerized services and a live dashboard.}

% Business application
\regbullet{\textbf{HOA management platform} — multi-tenant Rails+React application with modules for dues, violations, residents, and public sites; role-based access, reporting, and React/Vite front-end with Inertia; built for production but not yet deployed to live HOAs.}
\end{itemize}

% =============================================================================
% TALKS & COMMUNITY SECTION - Professional Involvement
% =============================================================================

\resumesection{TALKS \& COMMUNITY}

\begin{itemize}[leftmargin=18pt,itemsep=1pt,topsep=0pt]
% Conference presentations and speaking engagements
\regbullet{\textbf{CUG 2025} — "Employing a Software-Driven Approach to Scalable HPC System Management."}

% Conference presentations and speaking engagements
\regbullet{\textbf{NLIT 2024} — "Employing DevOps in HPC Operational Management."}

% Workshop and program leadership
\regbullet{\textbf{ORNL Pathways to Computing Internship Program} — Workshop Chair, 2022--present.}

% Conference committee involvement
\regbullet{\textbf{PEARC Conference} — Student Program Committee Chair, 2021--present.}
\end{itemize}

% =============================================================================
% DOCUMENT END
% =============================================================================

\end{document}
